###I- Applying Computational Tools R

#Question 1

#(a & b)

#Read and Skip First 6 Rows
dataset_laucnty14 <- read.csv(file="~/Desktop/DATA200HW3/Canvas/Data/laucnty14.csv", skip = 6, header = F)

dataset_laucnty15 <- read.csv("~/Desktop/DATA200HW3/Canvas/Data/laucnty15.csv", skip = 6, header = F)

dataset_laucnty16 <- read.csv("~/Desktop/DATA200HW3/Canvas/Data/laucnty16.csv", skip = 6, header = F)

dataset_laucnty17 <- read.csv("~/Desktop/DATA200HW3/Canvas/Data/laucnty17.csv", skip = 6, header = F)

dataset_laucnty18 <- read.csv("~/Desktop/DATA200HW3/Canvas/Data/laucnty18.csv", skip = 6, header = F)

#Set Column Names
col_dataset_laucnty14 <- setNames(dataset_laucnty14, c("LAUS Code","State FIPS Code","County FIPS Code","County Name/State Abbreviation","Year", "","Labor Force","Employed","Unemployed","Unemployment Rate %"))

col_dataset_laucnty15 <- setNames(dataset_laucnty15, c("LAUS Code","State FIPS Code","County FIPS Code","County Name/State Abbreviation","Year", "","Labor Force","Employed","Unemployed","Unemployment Rate %"))

col_dataset_laucnty16 <- setNames(dataset_laucnty16, c("LAUS Code","State FIPS Code","County FIPS Code","County Name/State Abbreviation","Year", "","Labor Force","Employed","Unemployed","Unemployment Rate %"))

col_dataset_laucnty17 <- setNames(dataset_laucnty17, c("LAUS Code","State FIPS Code","County FIPS Code","County Name/State Abbreviation","Year", "","Labor Force","Employed","Unemployed","Unemployment Rate %"))

col_dataset_laucnty18 <- setNames(dataset_laucnty18, c("LAUS Code","State FIPS Code","County FIPS Code","County Name/State Abbreviation","Year", "","Labor Force","Employed","Unemployed","Unemployment Rate %"))

#(c)

#Filering Columns
library(dplyr) 

drop_dataset_laucnty14 <-select (col_dataset_laucnty14 ,-c("LAUS Code","County Name/State Abbreviation", "","Labor Force","Employed","Unemployed"))

drop_dataset_laucnty15 <-select (col_dataset_laucnty15 ,-c("LAUS Code","County Name/State Abbreviation", "","Labor Force","Employed","Unemployed"))

drop_dataset_laucnty16 <-select (col_dataset_laucnty16 ,-c("LAUS Code","County Name/State Abbreviation", "","Labor Force","Employed","Unemployed"))

drop_dataset_laucnty17 <-select (col_dataset_laucnty17 ,-c("LAUS Code","County Name/State Abbreviation", "","Labor Force","Employed","Unemployed"))

drop_dataset_laucnty18 <-select (col_dataset_laucnty18 ,-c("LAUS Code","County Name/State Abbreviation", "","Labor Force","Employed","Unemployed"))

#(d)
#Append 5 Years

laucnty_14_18 <- bind_rows(drop_dataset_laucnty14,drop_dataset_laucnty15,drop_dataset_laucnty16,drop_dataset_laucnty17,drop_dataset_laucnty18)

library(readr) 
readr::write_csv(x = laucnty_14_18, path = "~/Desktop/DATA200HW3/Canvas/Data/laucnty_14_18.csv")

#(e)
#Summary Statistics Unemployement Rate By Year
library(tidyverse)

     
```{r}
laucnty_14_18  %>%  
filter(
  !is.na(Year)
) %>% 
  group_by(Year) %>% 
  rename(
    unemployment_rate_pct = `Unemployment Rate %`
) %>% 
  summarise(min = min(unemployment_rate_pct),
         
            median = median(unemployment_rate_pct),
            
            mean= mean(unemployment_rate_pct),
            
            sd = sd(unemployment_rate_pct),
            
            max = max(unemployment_rate_pct)    
            
            )

```
            

#Question 2

```{r}

library(ggplot2)


a <- ggplot(data=laucnty_14_18 , aes(x=unemployment_rate_pct, y=mean(unemployment_rate_pct), group=1)) +
  geom_line()+
  geom_point()
a

```


library(ggplot2)
library(tidyverse)

laucnty_14_18  %>%  
  rename(
    unemployment_rate_pct = `Unemployment Rate %`
) %>% 
  
a <- ggplot(data=laucnty_14_18 , aes(x=unemployment_rate_pct, y=mean(unemployment_rate_pct), group=1)) +
  geom_line()+
  geom_point()
a
